---
title: "3 Million Tweet Analysis"
author: ""
date: "January 27, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

# Integration and cleaning

## Integration of Dataset

```{r}
library(data.table)
library(tidyverse)
#install.packages('bit64')

data <-  fread(input = 
    "D:/Columbia/Spring 2019/Data Science and Public Policy/Data Assignment 1/IRAhandle_tweets_1.csv")
data$alt_external_id <- as.character(data$alt_external_id) 
data$tweet_id <- as.character(data$tweet_id) 
for (i in 2:13)
{
  filename <- 
  paste("D:/Columbia/Spring 2019/Data Science and Public Policy/Data Assignment 1/IRAhandle_tweets_",
        i,".csv",sep = "")
  data1 <-  fread(input = filename)
  data1$alt_external_id <- as.character(data1$alt_external_id)
  data1$tweet_id <- as.character(data1$tweet_id) 
  data <- rbind(data,data1)
}
```

## Attributes and size in the dataset

The Attributes in the dataset are
```{r}
names(data)
```

The number of tweets in the dataset are
```{r}
nrow(data)
```


# Preliminary analysis

## All Category types
```{r}
# All Category types
acc_cat_data = data[,.(count = .N), by = "account_category"]
ggplot(acc_cat_data, aes(x = reorder(account_category, count), 
                         y = count, fill = account_category)) + 
  geom_bar(stat = 'identity') +
theme(axis.ticks = element_blank(),plot.title = element_text(size = rel(1.2)),
      legend.position="none") +
  labs(x = "Twitter Account Types", y = "Number of Tweets",
       title = "Number of tweets by different account types") + 
  guides(colour=FALSE) +
  coord_flip()
```

## Non English Category
```{r}
# Non English Category
non_eng_category = data[account_category == "NonEnglish",
                        .(count = .N), by = "account_type"]
ggplot(non_eng_category, aes(x = reorder(account_type, desc(count)),
                             y = count, fill = account_type)) + 
  geom_bar(stat = 'identity') +
  theme(axis.ticks = element_blank(),plot.title = element_text(size = rel(1.2)),
        legend.position="none") +
  labs(x = "Non English Tweet languages", y = "Number of Tweets",
       title = "Number of tweets by non english Language")+ 
  guides(colour=FALSE)
```


## Retweets Percentages
```{r}
# Retweets Percents
data_counter = data[(account_category == "RightTroll" | account_category == "LeftTroll"),
                    .(count = .N),by = "account_category"]
retweet_counter = data[(account_category == "RightTroll" | account_category == "LeftTroll") & 
                         post_type == "RETWEET",.(rtcount = .N),by = "account_category"]

merge.data.frame(data_counter, retweet_counter,account_category=account_category) %>%
  mutate(percent_retweet = rtcount *100 / count)

```

## Top Retweeters

```{r}
# Top Retweeters
retweeters = head(data[(account_category == "RightTroll" | account_category == "LeftTroll") & 
            post_type == "RETWEET",.(rtcount = .N),
            by = c("author", "account_category")][order(rtcount, decreasing = TRUE)],n = 10)
retweeters
```

Lets analyse AMELIEBALDWIN as the user has most retweets

```{r}
ame_bal_data <- data[author == "AMELIEBALDWIN", .(author, publish_date, content)]  
ame_bal_data[,.(count = .N), by = "publish_date"][count>5][order(count, decreasing = TRUE)]

```
The number of time AMELIEBALDWIN has tweeted more than 5 tweet a min is 821

## Fastest Retweeters
```{r}
# Fastest Retweeters
retweeters = head(data[(account_category == "RightTroll" | account_category == "LeftTroll") & 
           post_type == "RETWEET",.(rtcount = .N),
           by = c("author", "account_category")][order(rtcount, decreasing = TRUE)],n = 10)
fastest <- data[(account_category == "RightTroll" | account_category == "LeftTroll") & 
                  post_type == "RETWEET", .(author, publish_date, content)]  
fastest[,.(count = .N), by = c("publish_date", "author")][order(count, decreasing = TRUE)]
```

## Fastest Orignal Tweeters
```{r}
# Orignal tweeters
f_tweeters = head(data[(account_category == "RightTroll" | account_category == "LeftTroll") & 
           post_type == "",.(Retweet_count = .N),
           by = c("author", "account_category")][order(Retweet_count, decreasing = TRUE)],n = 10)
f_tweeters
fastest <- data[(account_category == "RightTroll" | account_category == "LeftTroll") & 
                  post_type == "", .(author, publish_date, content)]  
fast_10 <- fastest[,.(count = .N), 
           by = c("publish_date", "author")][count>10][order(count, decreasing = TRUE)]
fast_10
```
3015 times has more that 10 "Orignal Tweets" been posted per min. WILLIAMS8KALVIN has 116 tweets per min, which makes a case for some of the accounts being bots and not human accounts

```{r}
fast_10[,.(times = .N), by= c("author")][order(times, decreasing = TRUE)]
```
There is a possiblility of these 122 accounts being bots 

# Main Analysis

```{r}
troll_data <- data[(account_category == "RightTroll" | account_category == "LeftTroll"),
                   .(date = as.Date(publish_date, format = "%m/%d/%Y %H:%M"), 
                      content, author, account_category)]
```

For the main analysis, we will be considering the Right and left wing trolls and concentrate on the Period during the Wikileaks documnents and The mood of right and left wing trolls. We hypothesize that the Russian trolls were trying to divided the democratic party by cashing in on the wikileaks document leak and trying to display negetive sentiment on Hilary Clinton, while trying to play up Bernie Sanders Supporters by encouraging them to vote against Hillary.

We will be analysing tweets from the period 1st of June 2016 to 31st of August 2016

```{r}
dnc_troll <- troll_data %>%
  subset((date >= as.Date("2016-06-01"))) %>%
  subset((date <= as.Date("2016-08-31")))
```

```{r}
troll_data_counter = 
  dnc_troll[(account_category == "RightTroll" | account_category == "LeftTroll"),
                                .(count = .N),by = "account_category"]
troll_data_counter
```

It is surprising that though the Overall data shows that the Right Troll tweets were about twice of Left Wing Trolls, the left troll accounts were more active in the period of June- August 2016


```{r}
dnc_bernie_left <- dnc_troll[account_category == "LeftTroll" &
                  (grepl("Bernie",content,ignore.case = TRUE) | 
                  grepl("Sanders",content,ignore.case = TRUE)),]
dnc_bernie_right <- dnc_troll[account_category == "RightTroll" & 
                  (grepl("Bernie",content,ignore.case = TRUE) | 
                  grepl("Sanders",content,ignore.case = TRUE)),]
dnc_hillary_left <- dnc_troll[account_category == "LeftTroll" & 
                  (grepl("Hillary",content,ignore.case = TRUE) | 
                  grepl("Clinton",content,ignore.case = TRUE)),]
dnc_Hillary_right <- dnc_troll[account_category == "RightTroll" & 
                  (grepl("Hillary",content,ignore.case = TRUE) | 
                  grepl("Clinton",content,ignore.case = TRUE)),]
```

We will be using the R Sentiment analysis package for the analysis. This package provide 3 kinds of sentiment and we will be using SentimentGI, which is based on sentiment on the words of Harvard-IV Dictionary

```{r}
# install.packages("SentimentAnalysis")
library(SentimentAnalysis)
bernie_left_score <- sum(analyzeSentiment(dnc_bernie_left[,content], 
                 language = "english", aggregate = NULL, removeStopwords = TRUE,
                 stemming = TRUE)[2])/nrow(dnc_bernie_left)
bernie_right_score <- sum(analyzeSentiment(dnc_bernie_right[,content], 
                     language = "english", aggregate = NULL, removeStopwords = TRUE,
                     stemming = TRUE)[2])/nrow(dnc_bernie_right)
hillary_left_score <- sum(analyzeSentiment(dnc_hillary_left[,content], 
                     language = "english", aggregate = NULL, removeStopwords = TRUE,
                     stemming = TRUE)[2])/nrow(dnc_hillary_left)
hillary_right_score <- sum(analyzeSentiment(dnc_Hillary_right[,content], 
                     language = "english", aggregate = NULL, removeStopwords = TRUE,
                     stemming = TRUE)[2])/nrow(dnc_Hillary_right)
cat("Sentiment of Bernie Sanders Among Left Trolls =", bernie_left_score)
cat("Sentiment of Bernie Sanders Among Right Trolls =", bernie_right_score)
cat("Sentiment of Hillary Clinton Among Left Trolls =", hillary_left_score)
cat("Sentiment of Hillary Clinton Among Right Trolls =", hillary_right_score)

```

## Popular Hashtags in the period
```{r}
right_troll <- dnc_troll[account_category == "RightTroll" & grepl("#", dnc_troll$content)]
left_troll <- dnc_troll[account_category == "LeftTroll" & grepl("#", dnc_troll$content)]

head(setDT(list(unlist(str_extract_all(right_troll$content, "#\\S+"))))[,
                  .(count = .N), by = "V1"][order(count, decreasing = TRUE)], n = 10)
head(setDT(list(unlist(str_extract_all(left_troll$content, "#\\S+"))))[,
                  .(count = .N), by = "V1"][order(count, decreasing = TRUE)], n = 10)
```




